---
title: "My First Markdown"
author: "Martin Hirsch"
date: "9/14/2019"
output: html_document
---

Bold - **Bold**  
Italics - _Italics_  
Italics the other way - *Italics*
Bold Italics - _**Bold**_

# Title
## Subtitle
### Section Title
#### Subsection Title

- Bullet List 1
- Bullet List 2
- Bullet List 3

* Bullet List 1
* Bullet List 2
* Bullet List 3

1. Ordered List 1
1. Ordered List 2
1. Ordered List 3

# ggplot
ggplot is soooooo cool..... lol..

```{r first_chunk}
gapminder <- read.table("gapminder.txt", header = TRUE)
head(gapminder)
```


# Plot
```{r Plot}
library(ggplot2)
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp, color = continent)) + 
  geom_point(shape = 17,size = 0.5) +
  scale_x_log10() +
  geom_smooth(method = "lm", size = 0.5)
```

# Hiding the code/editing stuff
```#({r Plot hidden, echo = FALSE, results = 'hide', eval = FALSE, warning=FALSE})
library(ggplot2)
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp, color = continent)) + 
  geom_point(shape = 17,size = 0.5) +
  scale_x_log10() +
  geom_smooth(method = "lm", size = 0.5)
```

# editing the Plot
```{r Plotz,fig.height=5, fig.width=7}
library(ggplot2)
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp, color = continent)) + 
  geom_point(shape = 17,size = 0.5) +
  scale_x_log10() +
  geom_smooth(method = "lm", size = 0.5)
```


#script and text in the same line
the mean life expectancy of Sweden is `r mean(gapminder[gapminder$country == "Sweden", "lifeExp"])`.